\newsection
\section*{РЕФЕРАТ}

Объем работы равен \formbytotal{page}{страниц}{е}{ам}{ам}. Работа содержит \formbytotal{figurecnt}{иллюстраци}{ю}{и}{й}, \formbytotal{tablecnt}{таблиц}{у}{ы}{}, \formbytotal{bibcnt}{библиографическ}{ий источник}{их источника}{их источников} и \formbytotal{imglistcnt}{лист}{}{а}{ов} графического материала. Количество приложений – 2. Графический материал представлен в приложении А. Фрагменты исходного кода представлены в приложении Б.

	Перечень ключевых слов: программно-информационная система, чат-бот, запрос, мессенджер,
представление, модель данных, модуль, метод, пользователь, сообщение. 
	 
Объектом разработки является программно-информационная система для конструирования чат-ботов для Telegram.

Целью выпускной квалификационной работы являлась разработка модуля управления шаблонами.

При проектировании и создании программной системы применялась парадигма объектно-ориентированного программирования.

	В процессе создания программной системы был разработан программный комплекс, разработаны методы и реализованы отправка, получение и обработка данных.
	
Данная программно-информационная система находится на стадии внедрения. Её можно использовать для помощи в группах и каналах в мессенджере Telegram.
\newpage
\selectlanguage{english}
\section*{ABSTRACT}
  
The volume of work is \formbytotal{page}{page}{}{s}{s}. The work contains \formbytotal{figurecnt}{illustration}{}{s}{s}, \formbytotal{tablecnt}{table}{}{s}{s}, \formbytotal{bibcnt}{bibliographic source}{}{s}{s} and \formbytotal{imglistcnt}{sheet}{}{s}{s} of graphic material. The number of applications is 2. The graphic material is presented in annex A. The fragment of the source code is provided in annex B.

List of keywords: software information system, chat bot, request, messenger, presentation, data model, classes, method, user, message. 

The object of development is a web application of a social media platform for placing digital images.

The purpose of the final qualifying work was to develop a module for inter- user interaction for this web application.

When designing and creating a software system, the object-oriented programming paradigm was used.

In the process of creating a software system, a software package was developed, methods were developed and the sending, receiving and processing of data was implemented.

This software information system is at the implementation stage. It can be used to help in groups and channels in the Telegram messenger.

\selectlanguage{russian}
